---
title: "Gender differnce in education in Turkey in 1998"
author: "Jiayi Zheng"
date: "04/10/2022"
output: pdf_document
abstract: The government of Turkey has been pushing education agenda since the 1950s.Because Turkey is a Muslim country, the world wants to know if there is any gender difference in education in Turkey in 1998.
bibliography: reference.bib
---
Website for github^[https://github.com/wholesomefcas/Turkey4]

```{r, echo=FALSE, include=FALSE, message=FALSE}
library(readxl)
library(tidyverse)
library(janitor)
library(tinytex)
```
```{r, echo=FALSE, include=FALSE, message=FALSE}
#cite the packages
citation("tidyverse")
citation("readxl")
citation("janitor")
print(citation("tinytex"), bibtex=TRUE)
citation("dplyr")
citation("ggplot2")
citation()
```


# 1 Introduction
The government of Turkey has been pushing education agenda since the 1950s. Because Turkey is a Muslim country, the world wants to know if there is any gender difference in education in Turkey in 1998.\

```{r, echo=FALSE, message=FALSE, include=FALSE}
cleaned_data <- read_csv("cleaned_data.csv")
```

# 2 Data 
The data is analysis and cleaned in R [@R1] using readxl [@P2], jenitor [@P3], the tidyverse [@P1], and dplyr packages [@P5] in the Rstudio.The paper is knitted in Rmarkdown.\

The data pdf is downloaded from [@A2]


# 3 Result

There is significant gender difference in education levels in Turkey in 1998. This result is from the conducted two-sample t test.

# 4 Appendix

```{r,message=FALSE,echo=FALSE}
colnames(cleaned_data)[11] <- "Type"
knitr::kable(cbind(cleaned_data[,11],cleaned_data[,1:4]))
```

```{r,message=FALSE,echo=FALSE}
knitr::kable(cbind(cleaned_data[,11],cleaned_data[,1],cleaned_data[,5:7]))
```

```{r,message=FALSE,echo=FALSE}
knitr::kable(cbind(cleaned_data[,11],cleaned_data[,1],cleaned_data[,8:10]))
```

# Reference
